Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-08-19 Ch1_movement_rates/Ch1_Appendix_A.Rmd
extra line
Fix parameters

for(m in 1:3){
  m.0 <- m.data[m]
  for(j in 1:n.individuals){
  for(k in 1:nruns){
  a <- sim_movement(m_2[j], plot.it = FALSE, return.data.frame = TRUE) %>% 
    mutate(indiv = as.factor(j),
           run = paste0("r_", k),
           pop.id = paste0("p_",m))
  df <- rbind.data.frame(df, a)
}
}

}

df %>% 
  ggplot(., aes(x = xloc, y=yloc, group = run, color = indiv)) +
  facet_wrap(~pop.id) +
  geom_path() +
  scale_color_manual(values = mycols) +
  theme_bw() +
  theme(legend.position = "bottom") +
  NULL
```

>>>>

for(m in 1:3){
  m.0 <- m.data[m]
  for(j in 1:n.individuals){
    for(k in 1:nruns){
      a <- sim_movement(m.0[j,], plot.it = FALSE, return.data.frame = TRUE) %>% 
        mutate(indiv = as.factor(j),
               run = paste0("r_", k),
               popu = paste0("p_",m))
      df <- rbind.data.frame(df, a)
    }
  }
}

df %>% 
  ggplot(., aes(x = xloc, y=yloc, group = run, color = indiv)) +
  facet_wrap(~popu) +
  geom_path() +
  scale_color_manual(values = mycols) +
  theme_bw() +
  theme(legend.position = "bottom") +
  NULL
```
